\section{Work Experience}
\textbf{Senior Analyst \(|\) Accenture} \hfill {Jun 2023 - present}

\resumeSubHeadingListStart

\resumeSubheading
{Operational Excellence Advisor} {Nov 2025 - present}\

\textbf{Tools and Technologies:}
Python, Django (APIs and serializers), PostgreSQL, JWT, RBAC, multithreading, multitenancy

\resumeItemListStart
\resumeItem{Designed and implemented RBAC-based authorization for tenant-aware access control, ensuring secure role separation across enterprise users.}
\resumeItem{Architected a Django-backed multitenant platform with PostgreSQL data partitioning to support isolated, scalable tenant data management.}
\resumeItem{Optimized backend throughput using multithreading and concurrent task execution, improving response times for high-volume operational workloads.}
\resumeItemListEnd

\resumeSubHeadingListStart

\resumeSubheading
{AI-Driven Financial Variance Insight System}{Jun 2024 - Nov 2025}\

\textbf{Tools and Technologies:}
Python, Django (APIs and serializers), LangChain (SQL generation module), Vertex AI (LLM orchestration), Postgres, BigQuery, Stored Procedures, GCP, IAM

\resumeItemListStart
\resumeItem{Developed a dual-service system for variance insight generation, including pre-generated insights and a natural language query service.}
\resumeItem{Designed and integrated a Python-based asynchronous job to fetch and store \textbf{10,000+ pre-generated insights} via API, enabling efficient dashboard rendering.}
\resumeItem{Implemented \textbf{parallel processing} using \texttt{asyncio} and \texttt{aiohttp}, reducing job execution time from \textbf{30 hours to 2.5 minutes}—a \textbf{720x performance improvement}.}
\resumeItem{Completed UAT successfully and transitioned the solution into production, ensuring stable adoption and operational readiness.}
\resumeItem{Leveraged \textbf{Vertex AI} for LLM orchestration to enhance natural language queries and automate SQL generation.}
\resumeItem{Implemented \textbf{SQL translation} for detailed variance analysis, utilizing \textbf{Postgres}, \textbf{BigQuery}, and \textbf{stored procedures} for optimized data handling.}
\resumeItem{Deployed the system securely on \textbf{Google Cloud Platform (GCP)}, with role-based access control using IAM.}

\resumeItemListEnd

\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\resumeSubheading
{OCR and LLM-Driven Invoice Reconciliation}{Apr 2023 - May 2024}\

\textbf{Tools and Technologies:} Python, FastAPI, PyPDF, Git, OCR, LLMs
\resumeItemListStart
\resumeItem{Automated extracting and verifying invoice data from scanned PDFs using \textbf{OCR} and \textbf{PyPDF} for efficient data handling.}
\resumeItem{Developed APIs using \textbf{FastAPI} to facilitate seamless integration of invoice validation functionalities.}
\resumeItem{Leveraged \textbf{LLMs} for natural language processing to accurately compare invoice details against transaction records.}
\resumeItem{Utilized \textbf{Git} for version control and collaborative development throughout the project lifecycle.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\resumeSubheading
{IBM AIF360 and GenAI Metrics Integration}{Dec 2023 - March 2024}\

\textbf{Tools and Technologies:} Python, AIF360, HuggingFace, Abstraction Methods, Generative AI Metrics
\resumeItemListStart
\resumeItem{Integrated \textbf{AIF360} and Generative AI evaluations into a Responsible AI (RAI) platform, significantly expanding its feature set.}
\resumeItem{Enhanced tools for model monitoring and quality assessment using \textbf{HuggingFace} and abstraction techniques.}
\resumeItem{Utilized \textbf{Python} for implementing scalable solutions and efficiently integrating AI metrics.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\resumeSubheading
{GenAI-Based Semantic Resume Ranking}{Aug 2023 - Nov 2023}\

\textbf{Tools and Technologies:} LLMs, ChromaDB, Vector Database, Django, Threading
\resumeItemListStart
\resumeItem{Developed a system enabling efficient candidate screening through semantic similarity matching between job descriptions and resumes.}
\resumeItem{Implemented resume processing, summarization, and vector database embeddings using \textbf{ChromaDB} to optimize candidate ranking and selection.}
\resumeItem{Leveraged \textbf{Django} for creating scalable APIs and utilized \textbf{threading} to accelerate embedding creation for resumes.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\textbf{Student Intern  \(|\) Siemens} \hfill {OCT 2023 - Mar 2023}\\

\hspace{1em}\textbf{Tools and Technologies:} C++, Python, VS Code 
\resumeItemListStart
\resumeItem{As part of the security team during my internship, I worked on identifying vulnerabilities within the Siemens NX CAD codebase. My role involved generating lists of files that contained specific keywords indicative of potential security risks. This allowed me to contribute to strengthening the codebase's security.}
\resumeItemListEnd
\resumeSubHeadingListStart



