\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Operational Excellence Advisor}{Nov 2025 -- Present}{}{}
\textbf{Tools and Technologies:} Python, Django, PostgreSQL, JWT, RBAC, Multithreading, Multitenancy
\resumeItemListStart
\resumeItem{Implemented tenant-aware RBAC authorization, ensuring secure role separation across 7 client organizations in the APAC region.}
\resumeItem{Architected a Django-based multitenant platform with PostgreSQL partitioning, delivering data isolation and compliance for each client.}
\resumeItem{Optimized backend throughput with multithreading, reducing response times from seconds to sub-second and enabling real-time monitoring for $\sim$100 agents and leads.}
\resumeItem{Delivered a performance monitoring tool that provided leadership with actionable insights into agent KPIs and lead conversion rates, enabling faster operational decisions.}
\resumeItemListEnd

\resumeSubheading
{AI-Driven Financial Variance Insight System}{Jun 2024 -- Nov 2025}{}{}
\textbf{Tools and Technologies:} Python, Django, LangChain, Vertex AI, Postgres, BigQuery, Stored Procedures, GCP, Tableau
\resumeItemListStart
\resumeItem{Built backend services powering a Tableau dashboard with 10,000+ pre-generated financial variance insights.}
\resumeItem{Engineered an async Python job with parallel processing, cutting execution time from 30 hours to 2.5 minutes (720x faster).}
\resumeItem{Created an initial demo POC for generating charts and insights on financial data, later expanded into a full production system adopted across APAC clients.}
\resumeItem{Integrated Vertex AI + LangChain to enable a chatbot for natural language queries on financial data (e.g., balance sheets, variance explanations).}
\resumeItem{Optimized SQL translation and variance analysis using Postgres, BigQuery, and stored procedures for efficient data handling.}
\resumeItem{Completed UAT and production rollout, achieving stable adoption and empowering leadership with actionable financial insights.}
\resumeItemListEnd

\resumeSubheading
{IBM AIF360 and GenAI Metrics Integration}{Dec 2023 -- Mar 2024}{}{}
\textbf{Tools and Technologies:} Python, AIF360, HuggingFace, Generative AI Metrics, Abstraction Methods
\resumeItemListStart
\resumeItem{Integrated IBM AIF360 and Generative AI evaluations into Accenture’s Responsible AI platform, expanding support for multi-vendor frameworks (AWS, Google, Azure, IBM).}
\resumeItem{Enhanced model monitoring and quality assessment using HuggingFace and abstraction techniques for scalable evaluation.}
\resumeItem{Implemented Python-based integrations to unify AI fairness and generative metrics, enabling holistic Responsible AI reporting.}
\resumeItemListEnd

\resumeSubheading
{GenAI-Based Semantic Resume Ranking (POC)}{Aug 2023 -- Nov 2023}{}{}
\textbf{Tools and Technologies:} LLMs, ChromaDB, Vector Database, Django, Threading
\resumeItemListStart
\resumeItem{Built a POC system for semantic similarity matching between job descriptions and resumes to streamline candidate screening.}
\resumeItem{Implemented resume processing, summarization, and vector embeddings with ChromaDB, enabling efficient ranking and selection.}
\resumeItem{Developed scalable APIs in Django and accelerated embedding creation using threading for faster processing.}
\resumeItemListEnd

\resumeSubHeadingListEnd
